Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-04-25 paper/ms.tex
Fix footnotes and figure labels

\usepackage{epsfig,caption}
\usepackage{color}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{longtable}
% \usepackage{amssymb}
\usepackage{rotating,xcolor}
\usepackage{hyperref}
% \usepackage{tgbonum}

@@

\let\thefootnote\relax\footnote{

@@

\end{affiliations}
}

@@

\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}
\captionsetup[figure]{labelformat=empty}
\renewcommand{\figurename}{Extended Data Figure}
\renewcommand{\thetable}{Extended Data \arabic{table}}

@@

After generating the gaseous disk in this way, we stitched the gas disk
together with the GALAKOS N-body disk (and bulge and dark matter halo) after
the GALAKOS disk has been allowed to evolve for $1.5\,\textrm{Gyr}$. The
purpose of allowing the GALAKOS disk to evolve first for a short period of
time is to allow for the bar to form unimpacted by the presence of the gas
(which would normally disrupt the formation of the bar). Throughout this work,
we consider $t=0$ for the N-body run to be the time at which we added the gas
phase for the SMUGGLE run (i.e. we ignore the first $1.5\,\textrm{Gyr}$ of
evolution of the N-body disk when the bar is forming). We made one additional
modification when stitching the gas disk together with the N-body disk - we
created a vacuum within the central $4\,\textrm{kpc}$. This vacuum guards
against an initial dramatic infall of gas within the bar region, which we
found to destroy the bar.

>>>>

\usepackage{epsfig,caption}
\usepackage{color}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{longtable}
% \usepackage{amssymb}
\usepackage{rotating,xcolor}
\usepackage{hyperref}
% \usepackage{tgbonum}
\usepackage[symbol]{footmisc}

@@

{\let\thefootnote\relax\footnote{

@@

\end{affiliations}
}}

% \renewcommand{\thefootnote}{\fnsymbol{footnote}}

@@

\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand{\figurename}{Extended Data Figure}
\renewcommand{\thetable}{Extended Data \arabic{table}}

@@

After generating the gaseous disk in this way, we stitched the gas disk
together with the GALAKOS N-body disk (and bulge and dark matter halo) after
the GALAKOS disk has been allowed to evolve for $1.5\,\textrm{Gyr}$. The
purpose of allowing the GALAKOS disk to evolve first for a short period of
time is to allow for the bar to form unimpacted by the presence of the gas
(which would normally disrupt the formation of the bar). Throughout this work,
we consider $t=0$ for the N-body run to be the time at which we added the gas
phase for the SMUGGLE run (i.e. we ignore the first $1.5\,\textrm{Gyr}$ of
evolution of the N-body disk when the bar is forming). We made one additional
modification when stitching the gas disk together with the N-body disk - we
created a hole within the central $4\,\textrm{kpc}$. This hole guards
against an initial dramatic infall of gas within the bar region, which we
found to destroy the bar.
